\documentclass[a4paper,headsepline,oneside,11pt]{scrartcl}
% for longer works like diploma theses maybe use
% \documentclass[a4paper,headsepline,11pt]{scrreprt}
% \documentclass[a4paper,headsepline,11pt]{scrbook}

\input{header} % put all your packages and own commands here; helps
               % keeping then document more clean
\input{glossary} % define all your acronyms here

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%v
% begin document

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% T I T L E P A G E
\include{titlepage/titlepage}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}
\label{sec:Abstract}
Provide an abstract; only text, no formulae; it will be copied into TISS.

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section*{Zusammenfassung}
%\addcontentsline{toc}{section}{Zusammenfassung}
%\label{sec:Zusammenfassung}

%Eine deutsche Zusammenfassung ist nicht unbedingt notwendig.

%\newpage

\tableofcontents

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction and Background}
\label{sec:introduction}
%
Introduce the topic of your thesis and provide an overview of previous work with references, e.~g. \cite{Stock2018} (required for a literature list -- references at the end of the document).

Be brief, the document excluding titlepage, abstract, table of contents and references should not exceed three pages.
%
\section{Aim and Research Question / Objective / Hypothesis}
\label{sec:aim}
%
Address the goals of the thesis and formulate the research question /
objective / hypothesis. Please adjust the title of this section
accordingly.
%
\section{Materials and Methods}
\label{sec:materials}
%
Outline the tools and methods you plan to use to achieve your research
goals.
%
\section{Expected Results}
\label{sec:results}
%
Briefly discuss the expected results and their impact.
%
\section{Structure of Thesis}
\label{sec:structure}
%
Make a coarse structure (index) of the planned thesis document:
% 
\begin{enumerate}
\item Section 1
  \begin{enumerate}
  \item Subsection
  \item \dots
  \end{enumerate}
\item Section 2
  \begin{enumerate}
  \item Subsection
  \item \dots
  \end{enumerate}
\item \dots
\end{enumerate}
% 
\section{Planned Timeline}
\label{sec:timeline}
%
Provide a coarse timeline for the thesis (table or other, as you prefer).
\begin{table}[htb!]
  \centering
  % \begin{adjustbox}{width=\textwidth}
  %   You can use adjustbox in case your table is too wide
  \caption{Planned timeline for thesis}
  \label{tab:timeline}
  \begin{tabularx}{\linewidth}{l|l}
    \toprule%\hline
    \textbf{Time} & \textbf{Activity}\\
    \midrule
    early March & e.~g. literature research; get familiar with the topic\\
    \midrule
    early April & e.~g. first measurements, or whatever is planned\\
    \midrule
    \dots & \dots\\
    \midrule
    November & e.~g. finish thesis and hand in\\
   \bottomrule
  \end{tabularx}
  % \end{adjustbox}
\end{table}
% \newpage
\FloatBarrier
\printbibliography[heading=bibintoc]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End: